---
title: "Assignment 7"
author: "Kaylar Fullington"
date: 2/12/2022
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Set the working directory to the root of your DSC 520 directory
setwd("C:/Users/runek/dsc520")
```{r echo = FALSE}
setwd("C:/Users/runek/dsc520")
```

## Load the `data/r4ds/heights.csv` to
heights_df <- read.csv("data/r4ds/heights.csv")
```{r echo = FALSE}
heights_df <- read.csv("data/r4ds/heights.csv")
```

# Fit a linear model
earn_lm <-  lm(earn ~ height + sex + ed + age + race, data = heights_df)
```{r echo = FALSE}
earn_lm <-  lm(earn ~ height + sex + ed + age + race, data = heights_df)
```

# View the summary of your model
summary(earn_lm)

predicted_df <- data.frame(earn = predict(earn_lm, earn_lm$earn), ed = heights_df$ed, race = heights_df$race, height = heights_df$height, age = heights_df$age, sex = heights_df$sex)

```{r echo = FALSE}
summary(earn_lm)

predicted_df <- data.frame(earn = predict(earn_lm, earn_lm$earn), ed = heights_df$ed, race = heights_df$race, height = heights_df$height, age = heights_df$age, sex = heights_df$sex)
```

## Compute deviation (i.e. residuals)
mean_earn <- mean(heights_df$earn)
```{r echo = FALSE}
heights_df <- read.csv("data/r4ds/heights.csv")
mean_earn <- mean(heights_df$earn)
mean_earn
```

## Corrected Sum of Squares Total
sst <- sum((mean_earn - heights_df$earn)^2)
```{r echo = FALSE}
sst <- sum((mean_earn - heights_df$earn)^2)
sst
```

## Corrected Sum of Squares for Model
ssm <- sum((mean_earn - predicted_df$earn)^2)
```{r echo = FALSE}
earn_lm <-  lm(earn ~ height + sex + ed + age + race, data = heights_df)
predicted_df <- data.frame(earn = predict(earn_lm, earn_lm$earn), ed = heights_df$ed, race = heights_df$race, height = heights_df$height, age = heights_df$age, sex = heights_df$sex)
ssm <- sum((mean_earn - predicted_df$earn)^2)
ssm
```

## Residuals
residuals <- heights_df$earn - predicted_df$earn
```{r echo = FALSE}
residuals <- heights_df$earn - predicted_df$earn
head(residuals)
```

## Sum of Squares for Error
sse <- sum(residuals^2)
```{r echo = FALSE}
sse <- sum(residuals^2)
sse
```

## R Squared
r_squared <- ssm / sst
```{r echo = FALSE}
ssm <- sum((mean_earn - predicted_df$earn)^2)
sst <- sum((mean_earn - heights_df$earn)^2)
r_squared <- ssm / sst
r_squared
```

## Number of observations
n <- nrow(heights_df)
```{r echo = FALSE}
n <- nrow(heights_df)
n
```

## Number of regression paramaters
p <- 8
```{r echo = FALSE}
p <- 8
p
```

## Corrected Degrees of Freedom for Model
dfm <- p - 1
```{r echo = FALSE}
dfm <- p - 1
dfm
```

## Degrees of Freedom for Error
dfe <- n - p
```{r echo = FALSE}
dfe <- n - p
dfe
```

## Corrected Degrees of Freedom Total:   DFT = n - 1
dft <- n - 1
```{r echo = FALSE}
dft <- n - 1
dft
```

## Mean of Squares for Model:   MSM = SSM / DFM
msm <- ssm / dfm
```{r echo = FALSE}
msm <- ssm / dfm
```

## Mean of Squares for Error:   MSE = SSE / DFE
mse <- sse / dfe
``{r echo = FALSE}
mse <- sse / dfe
mse
```

## Mean of Squares Total:   MST = SST / DFT
mst <- sst / dft
```{r echo = FALSE}
mst <- sst / dft
mst
```

## Adjusted R Squared R2 = 1 - (1 - R2)(n - 1) / (n - p)
adjusted_r_squared <- 1 - (1 - r_squared) * (n - 1) / (n - p)
```{r echo = FALSE}
adjusted_r_squared <- 1 - (1 - r_squared) * (n - 1) / (n - p)
adjusted_r_squared
```
